cardinalR: Generating interesting high-dimensional data structures

### 2025-08-22 paper-cardinalR.Rmd
Updated figure1

A branching structure captures trajectories that diverge or bifurcate from a common origin, similar processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometry, number of points, and the number of branches. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.

@@

linearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

linearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

linearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orgcurvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orgcurvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orgcurvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r, label = "fig-orgcurvybranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches`, `linearbranches`, `curvybranches`, `orglinearbranches`, `orgcurvybranches` data.", fig.width=15, fig.height=25}

>>>>

A branching structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:overviewhtml)"} else { "Figure \\@ref(fig:branch-proj)"})`) captures trajectories that diverge or bifurcate from a common origin, similar processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometry, number of points, and the number of branches. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.

@@

linearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "b1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

linearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

linearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "c1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "c2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "c3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "d1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orgcurvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "e1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orgcurvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "e2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orgcurvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "e3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r branch-proj, fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.", fig.width=15, fig.height=25}

### 2025-08-22 paper-cardinalR.tex
Updated figure1

A branching structure captures trajectories that diverge or bifurcate from a common origin, similar processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometry, number of points, and the number of branches. Table \ref{tab:branching-tb-pdf} outlines these functions. The main arguments of the functions described in Table \ref{tab:arg-branching-tb-pdf}.

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-orgcurvybranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `expbranches`, `linearbranches`, `curvybranches`, `orglinearbranches`, `orgcurvybranches` data.}\label{fig:fig-orgcurvybranches-proj}
\end{figure}

>>>>

A branching structure (Figure \ref{fig:branch-proj}) captures trajectories that diverge or bifurcate from a common origin, similar processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometry, number of points, and the number of branches. Table \ref{tab:branching-tb-pdf} outlines these functions. The main arguments of the functions described in Table \ref{tab:arg-branching-tb-pdf}.

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.}\label{fig:branch-proj}
\end{figure}
